Measurement Clusterization in D-optimal Designs for Bayesian Linear Inverse Problems

### 2023-05-05 latex/intro.tex
Moved example to appendix, added questions and answers in intro.

\section{Introduction}\label{section:OED intro}
Experimental design is an important part of many scientific
investigations. When considering an inverse problem, one can often
specify sensor locations (e.g.\ in electricat impedance tomography
\cite{horesh2010impedance}), certain wavelengths (e.g.\ in MRI
\cite{horesh2008mri}), or location of sensors for waves reflecting
from the ground (e.g.\ searching for oil \cite{horesh2008borehole} or
using a radar). Whatever the allowed set of measurements is, one
should select the optimal observations to take, in order to increase
accuracy, reduce costs, or both.

A set of measurements is called a \emph{design}, and an \emph{optimal
design} is found by optimizing some \emph{design
criterion}. Surprisingly, optimal designs sometimes result in
measuremets that are very similar. For example consider measurements
taken by sensors that evaluate some function at $\x \in \Omega
\subseteq \R^d, d=1,2,3$. An optimal design may place sensors in very
close proximity to each other (Figure \ref{fig:clusterization
  illustration}). Following \cite{Ucinski05}, we refer to this
phenomenon as \emph{sensor clusterization}.

There is a consensus among researchers that sensor clusterization is
undesirable. Some authors acknowledge the problem of sensor
clusterization and suggest remedies \cite{fedorov1996, hooker2009,
  fedorov2012, Ucinski05, neitzel2019sparse}. Others bypass the
problem by allowing sensor locations to be chosen from a coarse finite
grid \cite{alexanderian2014sparsification,
  AlexanderianPetraStadlerEtAl16, alexanderian2018efficient,
  koval2020, attia2020}, thus eliminating the possibility of sensor
clusterization. Sadly, there is no free lunch, and choosing sensor
locations from a coarse finite grid requires solving a hard
combinatorial optimization problem. The current study is the first, to
my knowledge, that aims to gain a deep understanding of sensor
clusterization.

\subsection{D-Optimal Designs}
In this study we focus on the Bayesian \emph{D-optimality} criterion
\cite{Chaloner1995}: a D-optimal design maximizes the expected
Kullback-Leibler divergence \cite{CoverThomas91} between posterior and
prior. For a linear model in finite dimensions, with Gaussian prior
and Gaussian noise, a D-optimal design minimizes the determinant of
the posterior covariance matrix\footnote{The frequentist version of
the D-optimality criterion aims to minimize the determinant of the
Fisher information matrix \cite[page 16]{Ucinski05}. For a linear
model with Gaussian noise, the Bayesian criterion is just
a regularized version of the frequentist criterion
\cite{Chaloner1995}.}.

Bayesian D-optimal designs for inverse problems on function spaces
were first studied by \cite{AlexanderianGloorGhattas14,
  AlexanderianPetraStadlerEtAl16,
  AlexanderianPetraStadlerEtAl14}. Similarly to the finite dimensional
case, a D-optimal design maximizes the KL divergence between posterior
and prior measures. For a linear inverse problem with Gaussian prior
and Gaussian noise, a D-optimal design minimizes an expression
analogous to the determinant of the posterior covariance operator
\cite{AlexanderianGloorGhattas14} (also \cref{thm:d optimality}
below).

Considerable effort focused on computational aspects of finding
optimal designs in infinite-dimensional Bayesian inverse problems.
Attia \cite{attia2020} focused on QoI, Koval considered model
uncertainty and focused on reducing forward and adjoint solves, using
randomized linear algebra.\cite{koval2020}.

\subsection{Remedies to Sensor Clusterization}
Several remedies to sensor clusterization were suggeted through the
years, and we will now overview some. In \emph{clusterization-free
design} locations are forced to be far from each other
\cite{Ucinski05}. This is achieved in a frequentist and
finite-dimensional setting, by either imposing distance constraints
between observations, or by introducing correlated errors which
account for both observation error and model error
\cite{Ucinski05}. Merging close measurements is also possible
\cite{fedorov2012}. Sensor clusterization is mitigated in time-series
analysis for pharmacokinetic experiments by modeling auto-correlation
time in the noise \cite{hooker2009}, and this approach is similar in
spirit to imposing error correlations as in \cite{Ucinski05}.

Many authors bypass the sensor clusterization problem by restricting
measurements to a coarse finite grid \cite{koval2020,
  AlexanderianPetraStadlerEtAl16, alexanderian2021, attia2020}, but
this practice has two flaws: First, using a coarse grid requires
solving a hard combinatorial optimization problem. Second, restricting
sensors to a such a small subset of the computatoinal domain will
necessarily give rise to sub-optimal designs. Several remedies were
offered for the first problem: Stadler suggested ell0
sparsification. Others suggested other stuff. None were offered for
the second.

%% Today, including model errors are a bona-fide????  standard in the
%% inverse problems community: \cite{attia2020}, \cite{koval2020},
%% \cite{Alexanderian2021} all empower their models.  Both studies
%% present numerical techniques for finding optimal designs when model
%% error is present. Both are restricted to linear inverse problems
%% (although in the latter the authors use their method on a nonlinear
%% problem by taking a Laplace approximation for the posterior). Both
%% find an optimal design by first solving a continuous problem for
%% sensor weights. Said solution is then sparsified to give a binary
%% design. Both studies are successful in the task of Bayesian
%% inversion. Neither \cite{attia2020}, nor \cite{koval2020} mention any
%% effect model errors can have on sensor clusterization.

\subsection{Contribution}
Any of the above mentioned approaches might serve as a remedy and push
sensors away from each other. Yet, none offers any insight as to why
clusterization occurs. Also, as better models are employed, model
error is decreased and the clusterization phenomenon will eventually
reappear. While these approaches are practical and help practitioners
avoid sensor clusterization, they do not provide insight as to why
sensors are clustering.

The current study aims to fill the gap of understanding sensor
clusterization in infinte dimensional Bayesian linear inverse
problems. We propose and study a relaxed and analytically tractable
model for D-optimal designs. Under this model, D-optimal designs are
solutions of a constrained optimization problem, formulated using
Lagrange multipliers. The Lagrange multipliers formulation allows us
to rigorously show how model error mitigates clusterization (Section
\ref{section:non vanishing}), and why designs that exhibit
clusterization are indeed optimal when no model error is considered.

As a byproduct, the Lagrange multipliers problem for no model error
results in a characterization of D-optimal designs. The key idea is
that a D-optimal design reduces uncertainties where they are highest
first. This is the conclusion of part (5) of Theorem \ref{thm:char},
which we state below and prove in Section \ref{section:vanishing}.

\begin{restatable}[D-optimal designs with vanishing model error]{theorem}{char}\label{thm:char}
  %% \begin{theorem}[D-optimal designs with vanishing model error]\label{thm:char}
  %% Let Notation \ref{not:setup}. Further, let

  Let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on $\hilp$,
    where $\prcov:\hilp \to \hilp$ is the prior covariance operator.
  \item $\obs: \hilo \to \mathbb{R}^m$ observation operator, where $m
    \in \mathbb{N}$ is the number of observations taken. 
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance,
    $\data = \obs \fwd \param + \eps$, where $\eps \in \mathbb{R}^m$
    is iid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality utility function
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \sigma^{-2} \prcov^{1/2} \fwd ^*
        \obs^* \obs \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
    in decreasing order of magnitude.
  %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \item $\obs$ a D-optimal design operator
    \begin{equation*}
      \obs = \argmax_{\|\meas_j\| = 1, j=1,\dots,m}\tar(\obs).
    \end{equation*}
  \end{itemize}

@@

One byproduct of the proof of Theorem \ref{thm:char} is a novel lemma
in linear algebra: We show how to decompose a symmetric positive
definite matrix $M$ as $M = AA^t$, where $A$ has unit norm columns
(Lemma \ref{lemma:lax}). We also generalize two lemmas from linear
algebra to infinite-dimensional settings: In Lemma \ref{lemma:MDL} we
prove a matrix determinant lemma in Hilbert spaces, and in Lemma
\ref{lemma:lax} we generalize a lemma \cite{Lax07} for calculating
$\frac{\der}{\der t} \log \det (I + X(t))$, where $X(t)$ is an
operator valued function.

\subsection{Limitations}\label{subsec:limitations}
The study presented here is not free from drawbacks. First, our
relaxed model does not correspond to any real-life problem. It is
generic enough to be analytically tractable, but one may argue it is
to far removed from any real application. To these claims I would
argue that Mathematicians have a long history of studying models that
are bare-bones simplifications of real systems, e.g. the Ising model
\cite{cipra1987} the Lorenz system \cite{brin}, and the SIR model
\cite{keeling2008}, to name a few. The second drawback of our model is
that we do not show rigorously that clusterization necessarily occurs,
we only show that it does not pose any obstruction to D-optimality.

\subsection{An Example of Clusterization}\label{subsec:example}
\begin{figure}
  \begin{tikzpicture}[thick, scale=1.3, every node/.style={scale=0.99}]
    \begin{axis}
      [
      title={Posterior Pointwise Standard Deviations and D-Optimal Sensor Locations},  
      xmin = 0,
      xmax = 3.14,
      xlabel = {$x$},
      ylabel = posterior std,
      ymin   = 0,
      %compat = 1.3,
      % ymax   = 130,
      % ytick = \empty,
      legend cell align=left,
      % legend style={at={(0.45,0.2)}}
      legend pos= outer north east 
      ]
      % \draw[black!30!white, thin] (50,0) -- (50,130);
      % 
      %% \addplot [thin, black, mark=none] table{stdv-heat-sens1-var1.txt};
      %% \addlegendentry{1 sensors};

      %% \addplot [thin, blue, mark=none] table{stdv-heat-sens2-var1.txt};
      %% \addlegendentry{2 sensors};

      %% \addplot [thin, red, mark=none] table{stdv-heat-sens3-var1.txt};
      %% \addlegendentry{3 sensors};

      \addplot [thin, green, mark=none] table{stdv-heat-sens4-var1.txt};
      \addlegendentry{4 sensors};

      \addplot [thin, purple, mark=none] table{stdv-heat-sens5-var1.txt};
      \addlegendentry{5 sensors};

      \addplot [thin, cyan, mark=none] table{stdv-heat-sens6-var1.txt};
      \addlegendentry{6 sensors};

    \end{axis}
  \end{tikzpicture}
  \caption{Sensor clusterization for inferring the initial condition
    of the 1D heat equation. Posterior pointwise standard deviations
    (lines) are plotted over the domain $[0, \pi]$, for varying
    numbers of sensors. Sensor locations (circles) were chosen to
    optimize the D-optimality criterion. Sensor clusterization occurs
    for six sensors. Only four observation locations are used --- two
    pairs of sensors are so close together they are
    indistinguishable.}
  \label{fig:clusterization illustration}
\end{figure}

For the purpose of illustration, consider a toy inverse problem ---
inferring the initial condition of the 1D heat equation in $[0,\pi]$
with a homogeneous Dirichlet boundary condition. Sensor clusterization
is clearly evident, see Figure \ref{fig:clusterization}.

The 1D heat equation with homogeneous Dirichlet boundary condition is:
\begin{subequations}\label{eq:heat equation}
  \begin{alignat}{2}
    u_t &= \Delta u &&\qquad \text{in } [0,\pi] \times [0,\infty),\\
      u &= 0 &&\qquad \text{on } \{0, \pi\} \times [0,\infty),\\
        u &= u_0 &&\qquad \text{on }[0,\pi] \times \{0\}.
  \end{alignat}
\end{subequations}

The goal is to infer the initial condition $u_0$. Model the initial
condition as $u_0 \sim \normal(0,\prcov)$, for $\prcov =
(-\Delta)^{-1}$ with a homogeneous Dirichlet boundary condition. Fix
some final time $T$ and denote by $\fwd$ the forward operator, so that
$u(\cdot, T) = \fwd u_0$. Let $\obs$ the observation operator, so that
$u(\x_j,T) = (\obs u)_j, j=1,\dots,m$. Assume iid centered Gaussian
observation error, so observations are given by $u(\x_j,T) +
\eps(\x_j)$ with $\eps(\x_j) \sim \normal(0, \sigma^2)$ iid, $\sigma^2
> 0$. The posterior covariance is known and depends only on $\prcov,
\fwd, \obs$ and $\sigma^2$ \cite{Stuart10} (see Section
\ref{section:prelim} and \eqref{eq:postcov} below). Finally, choose
$\x_j,j=1,\dots,m$ to optimize the D-optimality criterion
\cite{AlexanderianGloorGhattas14}.

Sensor clusterization is illustrated in Figure \ref{fig:clusterization
  illustration}. The posterior covariance does not depend on data, so
the plot has no reference to actual data observed. The posterior
covariance does depend on location of the observation taken, which
were chosen to optimize the D-optimality criterion. Sensor
clusterization is clearly seen for six sensors; it looks like only
four observations were taken. Two pairs of sensors are clustered so
close together that they are indistinguishable from each other.

%% A D-optimal design
%% is found via a generalization of the D-optimality criterion to
%% infinite dimension(also, Section
%% \ref{subsec:D optimal design} below).

>>>>

\section{Introduction}\label{section:intro}
Measurements play a fundamental role in generating observations and
are indispensable to any inference process. In the realm of data
science, selecting the optimal set of measurements holds particular
significance when inferring parameters of a physical process. Unlike
many other fields, where measurements are fixed or limited, in this
context, we have the freedom to choose which measurements to take. We
would like to take advantage of this freedom to choose measurements
that enhance accuracy, reduce costs, or achieve both objectives
simultaneously. Whether measurements involves specifying electrode
locations on the skin in electric impedance tomography
\cite{horesh2010impedance}, determining certain wavelengths in MRI
\cite{horesh2008mri}, or positioning sensors for detecting
ground-reflected waves in the search for oil
\cite{horesh2008borehole}, the selection of optimal measurements,
referred to as the problem of \emph{optimal design}, becomes
crucial. To achieve this, researchers optimize specific \emph{design
criteria}, with A- and D-optimality being two of the most widely
recognized and extensively studied design criteria
\cite{Chaloner1995}.

Interestingly, A- and D-optimal designs have been observed to yield
remarkably similar measurements in certain cases \cite{fedorov1996,
  hooker2009, fedorov2012, Ucinski05, neitzel2019sparse}. To
illustrate this point, we consider a toy inverse problem: inferring
the initial condition of the 1D heat equation (details in Section
\ref{section:example}). In Figure \ref{fig:clusterization
  illustration} D-optimal measurement locations are shown for
different numbers of allowed measurements. Notably, for six
measurement locations, the D-optimal design yields two sets of
measurements that are almost indistinguishable from one another. This
intriguing phenomenon is known as \emph{measurement clusterization}
\cite{Ucinski05}, and we refer to a design that exhibits measurement
clusterization as a \emph{clustered design}.

\begin{figure}
  \begin{tikzpicture}[thick, scale=1.3, every node/.style={scale=0.99}]
    \begin{axis}
      %% title={Posterior Pointwise Standard Deviations and D-Optimal
      %% Measurement Locations}
      [xmin = 0, xmax = 3.14, xlabel = {$x \in \Omega$}, ylabel =
        posterior pointwise std, ymin = 0,
      %compat = 1.3,
      % ymax   = 130,
      % ytick = \empty,
      legend cell align=left,
      % legend style={at={(0.45,0.2)}}
      legend pos= outer north east 
      ]
      % \draw[black!30!white, thin] (50,0) -- (50,130);
      % 
      %% \addplot [thin, black, mark=none] table{stdv-heat-sens1-var1.txt};
      %% \addlegendentry{1 measurements};

      %% \addplot [thin, blue, mark=none] table{stdv-heat-sens2-var1.txt};
      %% \addlegendentry{2 measurements};

      %% \addplot [thin, red, mark=none] table{stdv-heat-sens3-var1.txt};
      %% \addlegendentry{3 measurements};

      \addplot [thin, green, mark=none] table{stdv-heat-sens4-var1.txt};
      \addlegendentry{4 measurements};

      \addplot [thin, purple, mark=none] table{stdv-heat-sens5-var1.txt};
      \addlegendentry{5 measurements};

      \addplot [thin, cyan, mark=none] table{stdv-heat-sens6-var1.txt};
      \addlegendentry{6 measurements};

    \end{axis}
  \end{tikzpicture}
  \caption{Measurement clusterization when inferring the initial
    condition of the 1D heat equation. Posterior pointwise standard
    deviations (lines) are plotted over the computational domain
    $\Omega = [0, \pi]$, for varying numbers of
    measurements. Measurement locations (circles) were chosen to
    according to the D-optimality criterion. Measurement
    clusterization occurs for six measurements: Only four measurement
    locations are visible, since two pairs of measurements are so
    close together they are indistinguishable.}
  \label{fig:clusterization illustration}
\end{figure}

Researchers widely agree that measurement clusterization is undesirable
\cite{fedorov1996, hooker2009, fedorov2012, Ucinski05,
  neitzel2019sparse}, prompting the exploration of various remedies to
address this issue. One approach involves merging ``close''
measurements \cite{fedorov2012}; however, this strategy merely
overlooks the phenomenon of measurement clusterization. An alternative
solution lies in \emph{clusterization-free design}s, where measurement
locations are deliberately chosen to be distant from one another. This
can be achieved by imposing distance constraints between measurements
or by introducing correlated errors that account for both observation
error and model misspecification \cite{Ucinski05}. For instance, in
the context of time-series analysis for pharmacokinetic experiments,
measurement clusterization can be mitigated by incorporating the modeling
of auto-correlation time within the noise terms
\cite{hooker2009}. %% This methodology shares a similar rationale with
%% the earlier approach, which assumed correlation between errors
%% \cite{Ucinski05}.

In spatial problems involving choice of measuremnts within a domain
$\Omega \subseteq \mathbb{R}^d, d=1,2,3$, many researchers circumvent
the problem of measurement clusterization by choosing measurements from a
coarse grid in $\Omega$ \cite{koval2020, alexanderian2021, attia2020,
  alexanderian2014, alexanderian2016,
  alexanderian2018efficient}. However, this approach incurs a
significant computational cost as it requires solving a difficult
combinatorial optimization problem to select optimal measurement
locations from a finite set. Typically, the optimization problem is
relaxed by first assigning optimal measurement "weights" in
$\mathbb{R}_+$ to potential measurement locations. Some authors
incorporate a sparsifying $\ell_1$ penalty term into the design
criterion, which is subsequently thresholded to achieve the desired
binary design \cite{horesh2008borehole}. Others progressively relax
the $\ell_1$ penalty to an $\ell_0$ penalty via a continuation method
\cite{alexanderian2016, alexanderian2014}. A clever alternative is to
cast the problem of finding optimal measurement weights as a stochastic
optimization problem \cite{attia2022stochastic}. All of the
aforementioned methods may indeed find a binary optimal design
restricted to a given coarse grid. However, none addresses one
fundamental issue: the restriction of measurement locations to a coarse
grid in $\Omega \subseteq \mathbb{R}^d, d=1,2,3$ inherently results in
a sub-optimal design.

Avoiding measurement clusterization is a pragmatic approach:
intuitively, we recognize that measurement clusterization is
undesirable, even though the underlying reasons may not be fully
clear. Consequently, we strive to prevent it and devise various
methodologies to avoid measurement clusterization. Yet each and every
one of these methodologies achieves this objective by imposing
restrictions on measurement locations, thereby fundamentally altering
the optimal design problem. Surprisingly, to the best of my knowledge,
no previous study has tried to address some seemingly simple yet
fundamental questions:
%
Why does measurement clusterization occur?
%
Why does imposing correlations between observations alleviate
measurement clusterization?
%
Should we aim to avoid measurement clusterization?
%
Can an optimal clustered design be relpaced with an equally optimal
non-clustered design?design?

\subsection{Contribution}
The primary objective of this study is to provide a comprehensive
understanding of measurement clusterization by addressing the
aforementioned questions. Our focus centers around investigating the
Bayesian D-optimality criterion, which involves maximizing the
expected Kullback-Leibler divergence between the posterior and prior
measures \cite{CoverThomas91, Chaloner1995}. To delve deeper into this
subject, we conduct an analysis of Bayesian D-optimal designs within
the context of linear inverse problems in Hilbert spaces. We propose a
novel relaxed model for D-optimality that maintains analytical
tractability and enables the identification of D-optimal designs using
Lagrange multipliers. This analytical framework facilitates the
exploration of the following questions posed at the end of the
previous paragraph:

\begin{enumerate}
\item \label{q:why} \textbf{Why does measurement clusterization
  occur?} In Section \ref{section:vanishing}, we provide an insightful
  explanation for the optimality of clustered designs when no model
  error is present. We demonstrate that measurement clusterization
  poses no obstruction to D-optimality and that clustered design are
  preferred by numerical algorithms.

  %% We conjecture that the prevalence of measurement clusterization
  %% arises due to the ease of discovering clustered designs.

\item \label{q:mitigate} \textbf{Why does imposing correlations
  between observations alleviate measurement clusterization?} In
  Section \ref{section:non vanishing}, we rigorously demonstrate the
  role of model error in mitigating clusterization, thereby
  corroborating earlier observations made by various researchers.

\item \label{q:avoid} \textbf{Should we aim to avoid measurement
  clusterization?} Based on the analysis conducted in this study, we
  did not find any compelling reason to explicitly avoid optimal
  clustered designs.

\item \label{q:replace} \textbf{Can an optimal clustered design be
  relpaced with an equally optimal non-clustered design?} In Section
  \ref{section:vanishing}, we answer this question in the affirmative,
  although we show that numerical experiments conducted using our
  model indicate a strong preference for clustered designs.
\end{enumerate}

The cornerstone of our investigation into measurement clusterization is
Theorem \ref{thm:char}, presented below and proven in Section
\ref{section:vanishing}. The key insight of Theorem \ref{thm:char}
lies in its fifth component, which highlights that a D-optimal design
aims to uniformly reduce posterior uncertainties across all posterior
covariance eigenvectors.

\begin{restatable}[D-optimal designs with vanishing model error]{theorem}{char}\label{thm:char}
  Let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on $\hilp$,
    where $\prcov:\hilp \to \hilp$ is the prior covariance operator.
  \item $\obs: \hilo \to \mathbb{R}^m$ measurement operator, where $m
    \in \mathbb{N}$ is the number of measurements taken.
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance,
    $\data = \obs \fwd \param + \eps$, where $\eps \in \mathbb{R}^m$
    is iid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality design criterion
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \sigma^{-2} \prcov^{1/2} \fwd ^*
        \obs^* \obs \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
    in decreasing order of magnitude.
  %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \item $\obs$ a D-optimal design operator
    \begin{equation*}
      \obs = \argmax_{\|\meas_j\| = 1, j=1,\dots,m}\tar(\obs).
    \end{equation*}
  \end{itemize}

@@

Other contributions include three useful lemmas: In Lemma
\ref{lemma:free} we decompose a symmetric positive definite matrix $M
\in \mathbb{R}^{k \times k}$ with $\ttr M = m \in \mathbb{N}$ as $M =
AA^t$, where $A$ has unit norm columns. In Lemma \ref{lemma:MDL} we
prove a matrix determinant lemma in Hilbert spaces. Finally in Lemma
\ref{lemma:lax} we generalize a lemma for calculating
$\frac{\der}{\der t} \log \det (I + X(t))$, where $X(t)$ is an
operator valued function \cite{Lax07}.

\subsection{Limitations}\label{subsec:limitations}
The main limitation of this study is that our generic model does not
correspond to any specific real-life problem. It is generic enough to
be analytically tractable, but one may argue it is too far removed
from any real application. To these claims I would argue that
scientists have a long history of studying models that are bare-bones
simplifications of real systems, e.g. the Ising model
\cite{cipra1987}, the Lorenz system \cite{brin}, the Lotka-Volterra
equations \cite{logan2006}, the Carnot engine \cite{kardar2007}, and
many others.

%% \subsection{An Example of Measurement Clusterization}\label{subsec:example}

### 2023-05-05 latex/paper.tex
Tryin to fix refs
Moved example to appendix, added questions and answers in intro.

\documentclass{siamonline220329}
%\documentclass{amsart}
\input{definitions}

@@

\title{Sensor Clusterization in D-optimal Designs for Bayesian Linear
  Inverse Problems}

@@

\date{\today}
\begin{document}
\maketitle
\begin{abstract}
  We investigate the problem of sensor clusterization in D-optimal
  experimental design for infinite-dimensional Bayesian linear inverse
  problems. Many authors seem to believe that the fact that spatial
  correlations mitigateWe suggest an analytically tractable model for D-optimal
  designs. We argue that sensor clusterization in the case of iid
  observation noise is generic. We also prove that a model error term
  mitigates the clusterization phenomenon.

@@

\bibliographystyle{siamplain}
\bibliography{/home/yair/projects/library.bib}

>>>>

\documentclass{siamonline220329}
%\documentclass{amsart}
%\documentclass{article}
\input{definitions}

@@

\title{Measurement Clusterization in D-optimal Designs for Bayesian Linear
  Inverse Problems}

@@

\date{\today}
\begin{document}
\maketitle
\begin{abstract}
  We investigate the problem of measurement clusterization in D-optimal
  experimental design for infinite-dimensional Bayesian linear inverse
  problems. Many authors seem to believe that the fact that spatial
  correlations mitigateWe suggest an analytically tractable model for D-optimal
  designs. We argue that measurement clusterization in the case of iid
  observation noise is generic. We also prove that a model error term
  mitigates the clusterization phenomenon.

@@

\bibliographystyle{siamplain}
%% %%\bibliographystyle{amsplain}
\bibliography{/home/yair/projects/library.bib}
